---
title: "Making bar chart using ggplot"
date: "2022-09-13"
---

# What is a bar chart?

A chart featuring the interaction of a categorical variable and it's numercial value. More simply, the numercial values are represented by bars, whose length vary based on the value

> Bar chart is more preferrable than pie charts and mostly better choice to compare values.

# When to use it?

* When drawing comparison between different categorical variables.
* When the discrete variables being represented are more than 4. 

# When not to use it?

* When the discrete variables being represented are greater than 5
* When comparison of a discrete variable, having another another discrete variable is required

# Hueristic of making a bar chart in R

* In the ggplot, aesthetic function call, 
     + x should be categorical variable. Use as.factor, in-case the variable is a numeric variable 
     + y should be the numerical variable from the dataset. 
     + Fill argument should be the categorical variable from dataset.
* Call geom_bar() function, wherein stat = "identity" 
  + Alterntively, geom_col() can also be used
* Finally, set labels using the labs() functions call 

# Examples of making bar chart using ggplot2

```{r}
library(tidyverse)
library(RColorBrewer)

```

Creating a sample data.

```{r}
df = tibble(
  brand = c("Samsung","Huawei","Apple","Xiaomi","OPPO","Other"),
  share = c(2090,1580, 1210, 930, 860, 3320)
  )

forcats::fct

```

## Bar chart


```{r}

ggplot(data = df |> fct_reorder(), 
       mapping = aes(x = brand, y = share)) +
  geom_bar(stat = "identity")


```



```{r}

# Move this to Abraj R File -----------------------------------------------
summary_obs <- tibble(
  rating = c("High", "Medium", "Low"),
  obs = c(0, 2, 7),
  color = c("red", "yellow", "green"),
  ann = c("No high rated exception", " ", " ")
  )

# summary_obs <- summary_obs %>%
#   mutate(
#     rating = factor(summary_obs$rating, levels = c("High", "Medium", "Low"))
#   )

summary_obs <- summary_obs %>%
  mutate(
    rating = as_factor(rating)
  )

ggplot(data = summary_obs, aes(x = rating, y = obs)) +
  geom_bar(stat = "identity", aes(fill = rating)) +
  geom_text(aes(label = obs)) +
  theme_minimal() +
  annotate("No high risk exception", x = 0.5, y =4) + 
  scale_fill_manual(values = c("red", "yellow", "green")) +
  labs(title = "Finance & Accounts Review",
       subtitle = "Summary of observations by rating",
       x = "Risk Rating",
       y = "No. of Observations"
       ) +
  theme(
    legend.position = "none"
  )

```



