---
title: "FIle management for R projects"
date: "2023-08-04"
---

# Reading files easily

Reading and writing files can sometimes be challenging. This is an attempt to share the process I am following for making it easy to reading and writing of files in R.

## Reading required packages.

```{r}
library(pacman)
pacman::p_load(fs, folderfun, tidyverse)

```

## Define the path wherein the input and output will be located in the local drive.

I have found the package [folder function package](https://cran.r-project.org/web/packages/folderfun/vignettes/intro.html) and [fs package](https://fs.r-lib.org/index.html) to be very useful for file managing files.

-   fs::path() will be used to construct the path of the location folder
-   folderfun::setff() will be used to define a new function, wherein the first argument is the name of the new function prceded by ff.

```{r}

# Defining the input function
folderfun::setff(name = 'In',
                 fs::path("C:/Users/aqureshi037/PycharmProjects/Ahsan_Blog_Quarto",
                          "posts", "file_n_folder_Mgmt", "input_data")
                 )

# Defining the ourput function
folderfun::setff(name = 'Out',
                 fs::path("C:/Users/aqureshi037/PycharmProjects/Ahsan_Blog_Quarto",
                          "posts", "file_n_folder_Mgmt", "output_data")
                 )


```

## Reading of the file

iris.csv file is already located in the 'input' folder.

```{r}

data(iris)

#Writing the data to the folder
readr::write_csv(iris, ffOut("iris.csv"))


#Reading the data from the folder
iris_data <- readr::read_csv(ffIn("iris.csv"))


```
