---
title: "Making pie chart using ggplot"
date: "2022-06-22"
---



# What is a pie chart?

A chart depicted by a circle, where the areas of the circle represent 100% proportion. To subdivide the circle into proportion, a line is drawn from axis to the circumference of circle - proportionate dividing the pie based on values.

> Pie charts are not recommended as a good visualization, rather we can use the bar plots instead.

# When to use it?

* When representing the proportion of values
* When drawing comparison between discrete variables and their aggregated values 
* When the discrete variables being represented are less than 4. Additionally, good labels are added.

# When not to use it?

* When the discrete variables being represented are greater than 5
* When comparison of a discrete variable, having another another discrete variable is required

Hueristic of making a pie chart in R

* In the ggplot, aesthetic function call, 
     + x should be empty 
     + y should be the numerical variable from the dataset. 
     + Fill argument should be the categorical variable from dataset.
* Call geom_bar() function, wherein stat = "identity" and width = 1 is defined.
* Call coord_polar() function with arguments ("y", start = 0)
* Put value text labels using, geom_text() and also position it correctly like this. geom_text(aes(label = paste0(round(share * 100), "%")), position = position_stack(vjust = 0.5))
* Put better colors for the fill argument in ggplot call like this. scale_fill_manual(values = c())
* Finally, eliminate all the labels using the labs() functions call and only specifying the title.

# Examples of making pie chart using ggplot2



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "static")

library(ggplot2)
library(RColorBrewer)
library(stringr)


```

Creating a sample data.

```{r data}
df = data.frame(brand = c("Samsung","Huawei","Apple","Xiaomi","OPPO","Other"),
            share = c(.2090,.1580,.1210,.0930,.0860,.3320))

```

## Donut chart


```{r}

ggplot(data = df, mapping = aes(x = "", y = share, fill = brand)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y", start = 0) +
  geom_text(aes(
    label = str_c(round(share*100), "%")),
    position = position_stack(vjust = 0.5)
    ) +
  theme_void() +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Manufacturer - Market Share") +
  theme(
    plot.title = element_text(hjust = 0.5, color = "red")
  )
```



```{r}
ggplot(data = df, mapping = aes(x = 2, y = share, fill = brand)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y", start = 0) +
  geom_text(aes(
    label = str_c(round(share*100), "%")),
    position = position_stack(vjust = 0.5)
    ) +
  theme_void() +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Manufacturer - Market Share") +
  theme(
    plot.title = element_text(hjust = 0.5, color = "red")
  ) +
  xlim(0.5, 2.5)
```


